---
title: "Project_Plan"
author: "Sofia Vazquez"
date: "3/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggplot2)
library(CausalImpact)
library(bsts)
```

# Plan

- Generate data
- Change BSTSM values for the Gaussian to see how they impact the performance.
- Create BSTSM with different state components. 

# Genarating Time Series Data
```{r}
M_t = 67
V_t = 5
Y= NULL

for (i in 1:1000){
  Y[i] <- M_t +  rnorm(n= 1, mean = 0, sd = 5)
  M_t  <- M_t + V_t + rnorm(n= 1, mean = 0, sd = 500)
  V_t  <- V_t + rnorm(n= 1, mean = 0.08, sd = 1)
}
Y
plot(Y, type = "l")
data_lin_trend<- data_frame(cov = Y + rnorm(1000, 0, 0.01), Y)
data_lin_trend$Y[800:1000] <- data_lin_trend$Y[800:1000]+20000

plot(data_lin_trend$Y, type = "l")

```
```{r}
data <- data_frame(y = Y) %>% mutate(x = 1:1000)
ggplot(data, aes(x = x, y = y))+
  geom_line()
```
# With seasonality

```{r}
# seasons <- 0:2
# initial_noise <- rnorm(1,0,1)
# gamma <- c(-3,2,1)
# mu    <- c(10,5,0)
# nita_perm <-c(rnorm(1,0,1), rnorm(1,0,2), rnorm(1,0,3)) 
# y = NULL
# 
# for (i in 0:3000-1){
#   current_season = round(i/3) #3 - i%%3
#   
#   y[i+1] <- mu[current_season] + rnorm(n= 1, mean = 0, sd = 1)
#   
#     nita[current_season] <- nita_perm[current_season] + rnorm(1,0,1)
#     
#   mu[current_season]  <- mu[current_season] +  nita[current_season]
# 
# }
# plot(y, type = "l")
# data_seasonal<- data_frame(cov = Y + rnorm(1000, 0, 0.01), Y)
# data_seasonal$Y[800:1000] <- data_seasonal$Y[800:1000]+20
```

Correct seasonal:
```{r}
M_t = 67
V_t = 5
G_t = c(-10,15,-5, 50, -20, -30,0)
Y= NULL
gamma_t = G_t[7]
for (i in 1:100){
  current_season <- length(G_t)- i%%length(G_t)
  
  Y[i] <- M_t +  rnorm(n= 1, mean = 0, sd = 1) + gamma_t
  M_t  <- M_t + V_t + rnorm(n= 1, mean = 0, sd = 1)
  V_t  <- V_t + rnorm(n= 1, mean = 0.08, sd = 1)
  gamma_t <- G_t[current_season] + rnorm(1,0,1)
}
Y
plot(Y, type = "l")
data_seasonal<- data_frame(cov = Y + rnorm(100, 0, 0.01), Y)
data_seasonal$Y[80:100] <- data_seasonal$Y[80:100] + 200
plot(data_seasonal$Y, type = "l")
```
# Running Causal impact on data with  trend
```{r RunCausalImpact}
pre.period <- as.Date(c("2019-01-01", "2021-03-11"))
post.period <- as.Date(c("2021-03-12", "2021-09-27"))
time.points <- seq.Date(as.Date("2019-01-01"), by = 1, length.out = 1000)
data <- zoo(cbind(data_lin_trend$Y#,data_lin_trend$cov
                  ), time.points)
impact <- CausalImpact(data, pre.period, post.period)
plot(impact)
```
# Running Causal impact on data with seasonality
```{r RunCausalImpact}
pre.period <- as.Date(c("2019-01-01", "2019-03-22"))
post.period <- as.Date(c("2019-03-23", "2019-04-11"))
time.points <- seq.Date(as.Date("2019-01-01"), by = 1, length.out = 100)
data <- zoo(cbind(data_seasonal$Y,data_seasonal$cov
                  ), time.points)
impact <- CausalImpact(data, pre.period, post.period)
plot(impact)
```
# Linear Model without regression and seasionality.
Plot is drawn to predict values for 20 future time points.
Created Pre-intervention period by slicing the data frame before the intervention(800)
COMMENT - Without regression the prediction is not accurate. Confidence intervals are pretty wide
```{r CreatingModels}
data_pre_intervention_lin = data_lin_trend[1:799,]
linear_only_state <- AddLocalLinearTrend(list(), data_pre_intervention_lin$Y)
model_linear <- bsts(data_pre_intervention_lin$Y,
               state.specification = linear_only_state,
               niter = 1000) #### LINEAR MODEL WITHOUT REGRESSION AND SEASIONALITY
pred_linear <- predict(model_linear, horizon = 200)
plot(pred_linear, plot.original = 800)
```
# Linear model with seasionality and regression
Plot is drawn to predict values for 20 future time points.
Created Pre-intervention period by slicing the data frame before the intervention(80)
COMMENT- Prediction when modelled properly seems to be close to true values, small confidence intervals
```{r linsesrigModed}
data_pre_seasonal = data_seasonal[1:79,]
linear_only_state <- AddLocalLinearTrend(list(), data_pre_seasonal$Y)
linear_seasonal_state <- AddSeasonal(linear_only_state, data_pre_seasonal$Y, nseasons = 7)
model_lin_season_regr <- bsts(Y ~ .,
               state.specification = linear_seasonal_state,
               niter = 1000,
               data = data_pre_seasonal) #### LINEAR MODEL WITH REGRESSION AND SEASIONALITY
pred_linear_seasonal_regr <- predict(model_lin_season_regr, horizon = 20,newdata = data_seasonal$cov[80:100])
plot(pred_linear_seasonal_regr, plot.original = 40)
```