---
title: "CausalImpact"
author: "Sai Koneru"
date: "3/2/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic usage of Causal impact copied from their website

```{r install}
library(CausalImpact)
set.seed(1)
x1 <- 100 + arima.sim(model = list(ar = 0.999), n = 100)
y <- 1.2 * x1 + rnorm(100)
y[71:100] <- y[71:100] + 10
data <- cbind(x1, y)
```
## Plotting the data created

```{r plot data, echo=FALSE}
matplot(data, type = "l")
```
## Run Causal Impact
```{r RunCausalImpact}
pre.period <- c(1, 70)
post.period <- c(71, 100)
impact <- CausalImpact(data, pre.period, post.period)
plot(impact)
```




## Reproducing Theoritical Simulation
Created two regression coefficients,two sinusoidal covariates and a local level
Initialized covariates to 1 and level to 0 as explained in the paper
Intervention occured at 389 days later by multiplying it with e
```{r Data_Creation}
library(CausalImpact)
set.seed(0)
data = NULL
linear_values = NULL
linear_values[1] = 0
beta1 = NULL
beta1[1] = 1
beta2 = NULL
beta2[1] = 1
cov1 = NULL
cov2 = NULL
cov1[1] = sin(pi/45)
cov2[1] = sin(pi/180)
for(i in 2:488){
  linear_values[i] = rnorm(n = 1,mean = linear_values[i-1],sd = 0.1)
  beta1[i] = rnorm(n = 1,mean = beta1[i-1],sd= 0.1)
  beta2[i] = rnorm(n = 1,mean = beta2[i-1],sd= 0.1)
  cov1[i] = sin((pi*i)/45)
  cov2[i] = sin((pi*i)/180)
}
output_true =20 + linear_values + rnorm(n = 1, mean = 0, sd = 0.1) + (cov1 * beta1) + (cov2 * beta2)
output_intervention = output_true 
output_intervention[389:488] = output_intervention[389:488]*exp(1)
```

## Running Causal Impact on simulated data

```{r RunCausalImpactonSimulatedData}
pre.period = c(1,389)
post.period = c(390,488)
data = cbind(output_intervention,output_true)
impact <- CausalImpact(data, pre.period, post.period)
plot(impact)
matplot(output_true,main = "True Output",col = "green",type = "l")
```

##TODO
Add dates to the x-axis which is causing some bugs
